Model matters with restricted Boltzmann machines

### 2017-01-16 presentations/uva/slides.Rmd
add uva slides

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | January 11, 2017
  |
  | Slides available at <http://bit.ly/kaplan-asu>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "January 11, 2017"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

@@

```{r acf, fig.cap="\\label{fig:acf}The autocorrelation functions (ACF) for the posterior probabilityies of all $2^4 = 16$ possible outcomes for the vector of $4$ visibles assessed at multiple lags for each method with BwTNLV in black and BwTNML in red.", fig.height=4.5, fig.width=8, out.width=".7\\linewidth"}
marginal_sample_good %>% 
  filter(iter > 50) %>%
  group_by(v1, v2, v3, v4, image_id) %>% 
  do(data.frame(acf = acf(.$prob, plot=FALSE)$acf,
     lag = acf(.$prob, plot=FALSE)$lag)) -> marginal_acfs

@@

all_statistics %>%
  gather(statistic, value, -iter, -method, -starts_with("v")) %>%
  filter(grepl("image", statistic) & !is.na(value)) %>%
  separate(statistic, into = c("junk", "statistic")) %>%
  mutate(statistic = factor(statistic, labels = paste("Image", 1:length(unique(statistic))))) %>%
  left_join(distn_emp %>% rename(prob_emp = prob) %>% right_join(distn_good %>% select(-image_id))) %>%
  ggplot() +
  geom_density(aes(value, y=..scaled.., colour = method, fill = method), alpha = .2) +
  geom_vline(aes(xintercept = prob)) +
  geom_vline(aes(xintercept = prob_emp), colour = "red") +
  facet_wrap(~statistic, scales = "free_x") + 
  ylab("Scaled Posterior Density") + xlab("Probability of Image") +
  scale_colour_discrete("Method", labels = c("Marginalized likelihood", "Trick prior")) +
  scale_fill_discrete("Method", labels = c("Marginalized likelihood", "Trick prior")) +
  theme(legend.position = "bottom") -> p.models
```

@@

* Slides -- <http://bit.ly/kaplan-asu>

>>>>

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | January 19, 2017
  |
  | Slides available at <http://bit.ly/kaplan-uva>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "January 19, 2017"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

@@

```{r acf, fig.cap="\\label{fig:acf}The autocorrelation functions (ACF) for the posterior probabilities of all $2^4 = 16$ possible outcomes for the vector of $4$ visibles assessed at multiple lags for each method with BwTNLV in black and BwTNML in red.", fig.height=4.5, fig.width=8, out.width=".7\\linewidth"}
marginal_sample_good %>% 
  filter(iter > 50) %>%
  group_by(v1, v2, v3, v4, image_id) %>% 
  do(data.frame(acf = acf(.$prob, plot=FALSE)$acf,
     lag = acf(.$prob, plot=FALSE)$lag)) -> marginal_acfs

@@

all_statistics %>%
  gather(statistic, value, -iter, -method, -starts_with("v")) %>%
  filter(grepl("image", statistic) & !is.na(value)) %>%
  separate(statistic, into = c("junk", "statistic")) %>%
  mutate(statistic = factor(statistic, labels = paste("Image", 1:length(unique(statistic))))) %>%
  left_join(distn_emp %>% rename(prob_emp = prob) %>% right_join(distn_good %>% select(-image_id))) %>%
  ggplot() +
  geom_density(aes(value, y=..scaled.., colour = method, fill = method), alpha = .2) +
  geom_vline(aes(xintercept = prob)) +
  geom_vline(aes(xintercept = prob_emp), colour = "red") +
  facet_wrap(~statistic, scales = "free_x") + 
  ylab("Scaled Posterior Density") + xlab("Probability of Image") +
  scale_colour_discrete("Method", labels = c("BwTNML", "BwTPLV")) +
  scale_fill_discrete("Method", labels = c("BwTNML", "BwTPLV")) +
  theme(legend.position = "bottom") -> p.models
```

@@

* Slides -- <http://bit.ly/kaplan-uva>
